Follow-up Samples

### 2016-12-08 submission/manuscript_outline_20161024.Rmd

***Differences in Adenoma and Carcinoma in Previously Associated Cancer Bacteria***
First, there was a clear magnitude difference in these specific OTUs based on whether they were from adenoma or carcinoma individuals [Figure 6].  The carcinoma samples showed a significant difference between initial and follow up samples for Peptostreptococcus assacharolytica (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas stomatis (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`) whereas there were no signficant differences in any of these OTUs in the adenoma samples [Table S5].

@@

**Figure 6: Previously Associated CRC Bacteria in Initial and Follow up Samples.**  A) Carcinoma initial and follow up samples. There was a significant difference in initial and follow up sample for the OTUs classfied as Peptostreptococcus assacharolytica (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas stomatis (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`).  B) Adenoma initial and follow up samples.  There were no significant differences between initial and follow up.

>>>>

***Differences in Adenoma and Carcinoma in Previously Associated Cancer Bacteria***
First, there was a clear magnitude difference in these specific OTUs based on whether they were from adenoma or carcinoma individuals [Figure 6].  The carcinoma samples showed a significant difference between initial and follow up samples for Peptostreptococcus stomatis (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas asaccharolytica (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`) whereas there were no signficant differences in any of these OTUs in the adenoma samples [Table S5].

@@

**Figure 6: Previously Associated CRC Bacteria in Initial and Follow up Samples.**  A) Carcinoma initial and follow up samples. There was a significant difference in initial and follow up sample for the OTUs classfied as Peptostreptococcus stomatis (P-value = `r format(pvalue_adn_crc_summary["pept", "crc_BH"], digits = 3)`) and Porphyromonas asaccharolytica (P-value = `r format(pvalue_adn_crc_summary["porp", "crc_BH"], digits = 3)`).  B) Adenoma initial and follow up samples.  There were no significant differences between initial and follow up.

### 2016-12-08 submission/manuscript_outline_20161024.tex

\textbf{\emph{Differences in Adenoma and Carcinoma in Previously
Associated Cancer Bacteria}} First, there was a clear magnitude
difference in these specific OTUs based on whether they were from
adenoma or carcinoma individuals {[}Figure 6{]}. The carcinoma samples
showed a significant difference between initial and follow up samples
for Peptostreptococcus assacharolytica (P-value = 0.0183) and
Porphyromonas stomatis (P-value = 0.0154) whereas there were no
signficant differences in any of these OTUs in the adenoma samples
{[}Table S5{]}.

@@

\textbf{Figure 6: Previously Associated CRC Bacteria in Initial and
Follow up Samples.} A) Carcinoma initial and follow up samples. There
was a significant difference in initial and follow up sample for the
OTUs classfied as Peptostreptococcus assacharolytica (P-value = 0.0183)
and Porphyromonas stomatis (P-value = 0.0154). B) Adenoma initial and
follow up samples. There were no significant differences between initial
and follow up.

>>>>

\textbf{\emph{Differences in Adenoma and Carcinoma in Previously
Associated Cancer Bacteria}} First, there was a clear magnitude
difference in these specific OTUs based on whether they were from
adenoma or carcinoma individuals {[}Figure 6{]}. The carcinoma samples
showed a significant difference between initial and follow up samples
for Peptostreptococcus stomatis (P-value = 0.0183) and Porphyromonas
asaccharolytica (P-value = 0.0154) whereas there were no signficant
differences in any of these OTUs in the adenoma samples {[}Table S5{]}.

@@

\textbf{Figure 6: Previously Associated CRC Bacteria in Initial and
Follow up Samples.} A) Carcinoma initial and follow up samples. There
was a significant difference in initial and follow up sample for the
OTUs classfied as Peptostreptococcus stomatis (P-value = 0.0183) and
Porphyromonas asaccharolytica (P-value = 0.0154). B) Adenoma initial and
follow up samples. There were no significant differences between initial
and follow up.
